---
title: "Tejesh Varma Maddana_MSBA_64060_Assignment -1"
author: "Tejesh Varma Maddana"
date: "2023-09-10"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```
#1.I have downloaded a dataset that has the data a mix of quantitative and qualitative(categorical) variables from the kaggle website and the source link is furnished below for your ready reference :
Dataset Source reference Link : https://www.kaggle.com/datasets/michau96/restaurant-business-rankings-2020

```{r}
#2. Importing the Data Set from the above referred souce
Food_Business <-  read.csv("~/Downloads/archive (3)/Restaurent.csv")
head(Food_Business)
```
#3(i) Printing the Descriptive Statistics of Quantitative Variables
```{r}
summary(Food_Business$Unit_Volume)
```
#3(ii) Printing the Descriptive Statistics of Categorical Variables 
```{r}
summary(Food_Business$Restaurant, Food_Business$Location)
```

#4. Transformation of a Quantitative Variable
```{r}
log_Unit_Volume = log(Food_Business$Unit_Volume)
log_Unit_Volume
```
```{r}
Food_Business$log_Unit_Volume <- c(log_Unit_Volume)
Food_Business$log_Unit_Volume
```
#5(i)Plot of one Quantitative Variable by considering the plot between number of restaurants in a particular city

```{r}
location_table = table(Food_Business$Location)

barplot(location_table,1:8 ,xlab = "Cities", ylab = "Number of Restaurants", main="Restaurant Count by Cities", col = rainbow(5))
```

#5(ii) Plot of ScatterPlot indicating number of restaurants in a particular city
```{r}
x = Food_Business$Sales
y = Food_Business$Unit_Volume

plot(x,y, xlab = "Sales", ylab = "Volume", main = "Restaurant Food Business Sales VS Volume", col = "blue")

```
